The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-10 src/paper/report.tex
Re-wrote answers re ref 1.

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
at least one day to be processed and there are aggregate capacity constraints. In
contrast, rapid antigen tests yield immediate results. Specificity and sensitivity of
these tests is set according to data analyzed in
\label{r.1.a}\Copy{r.1.a}{\cite{Bruemmer2021,Scheiblauer2021,Özcürümez2021};
    sensitivity depends on the timing of the test relative to the onset of infectiousness.}
After a phase-in period, all tests that are demanded will be performed.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand. Schools may
require staff and students to be tested regularly. Rapid tests may be offered by
employers to on-site workers. Individuals may demand tests for private reasons, which
include having plans to meet other people, showing symptoms of CoViD-19, and a household
member having tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid
tests.\footnote{Positive test results or symptoms lead most individuals to reduce their
    contacts; this is why tests impact the actual contacts in
    Figure~\ref{fig:model_description}.}

>>>>

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
at least one day to be processed and there are aggregate capacity constraints. In
contrast, rapid antigen tests yield immediate results.
\label{r.1.a}\Copy{r.1.a}{Specificity and sensitivity of these tests is set according to
data analyzed in \citet{Bruemmer2021,Scheiblauer2021,Özcürümez2021}; sensitivity depends
on the timing of the test relative to the onset of infectiousness as in
\citet{Smith2021}. We provide a robustness to different assumptions in
Appendix~\ref{subsec:robustness_rapid_test_sensitivity}.} After a phase-in period, all
tests that are demanded will be performed. Figure~\ref{fig:model_rapid_tests} shows our
model for rapid test demand. Schools may require staff and students to be tested
regularly. Rapid tests may be offered by employers to on-site workers. Individuals may
demand tests for private reasons, which include having plans to meet other people,
showing symptoms of CoViD-19, and a household member having tested positively for the
virus. We endow each agent with an individual compliance parameter. This parameter
determines whether she takes up rapid tests.\footnote{Positive test results or symptoms
lead most individuals to reduce their contacts; this is why tests impact the actual
contacts in Figure~\ref{fig:model_description}.}

### 2022-03-10 src/rev1_reply_comments.tex
Re-wrote answers re ref 1.

\response{%
    We would like to thank the reviewer for these insightful comments. First of all, we
    agree that the references we used have become outdated in the meantime. Note that we
    submitted the original manuscript in early September 2021; the analysis had been
    finalised in June already.

    Many thanks for pointing out that we misclassified the Quidel SARS Sofia antigen
    FIA test; we removed the reference.{\bf \color{red}DOUBLE-CHECK -- this is Smith2021}

    Indeed, in the line of the additional evidence, the numbers we use for test
    sensitivity seem to be in the upper part of plausible values. On
    page~\pageref{r.1.a} of the paper, we cite the two references you pointed out
    (numbering of references relates to this document):

@@

    We followed your suggestion and ran additional analyses with more conservative
    assumptions on the sensitivity of rapid tests. The results are very robust. We write
    in the main text on page~\pageref{r.1.b}

@@

    The robustness is due to the fact that over the course of an infection, the largest differences between the parameters we use in our main analysis and those based on other studies are found during the later stages of an infection. Uncovering an infection that was previously undetected at that stage does
    not have a large effect on subsequent infection dynamics. Our whole analysis in
    Appendix~\ref{subsec:robustness_rapid_test_sensitivity} reads as follows:

@@

Furthermore, I recommend including a declaration of potential conflicts of interest in
the manuscript. This may be particularly important in light of the significance of the
findings from the study for the continued operation of industrial companies.

\response{We have added such a declaration. There are no competing interests.}

@@

              Many thanks for this comment. Ideally, we would of course use real-time data. For example, several studies have used smartphone tracking data for this purpose. However, they are not detailed enough for our requirements, because they do not provide any information about \textit{who} is meeting with each other. These dimensions make up our contact networks, which are absolutely crucial.

>>>>

\response{%
    We would like to thank the reviewer for these insightful comments. First of all, we
    agree that the references we used have become outdated in the meantime. Note that we
    submitted the original manuscript in early September 2021; the analysis had been
    finalised in June of last year. Indeed, in the line of the additional evidence, the
    numbers we use for test sensitivity appear to be in the upper part of plausible
    values. We have followed your suggestion and report detailed robustness analyses in
    the paper and its Appendix.

    Before describing our changes, we would like to thank you for pointing out that the
    test analysed in \citet{Smith2021} is not a rapid test. While this is true, the
    crucial feature in \citet{Smith2021} is that the paper reports the sensitivity over
    the course of an infection. We have not found a comparable study. Getting this
    profile right is important particularly in the beginning of an infection, as we
    detail shortly. At that point, the differences between different methods to assess
    test sensitivity by timing within an infection are relatively small.

    On page~\pageref{r.1.a} of the paper, we cite the references you pointed out
    (numbering of references relates to this document) and note that we conduct a
    robustness analysis:\\[1ex]

@@

    We followed your suggestion and ran additional analyses with more conservative
    assumptions on the sensitivity of rapid tests. The results are very robust. We write
    in the main text on page~\pageref{r.1.b}:\\[1ex]

@@

    The robustness is due to the fact that over the course of an infection, the largest
    differences between the parameters we use in our main analysis and those based on
    imputing values from other studies are found during the later stages of an
    infection. Uncovering an infection that was previously undetected at that stage does
    not have a large effect on subsequent infection dynamics. Our whole analysis in
    Appendix~\ref{subsec:robustness_rapid_test_sensitivity} reads as follows:\\[1ex]

@@

~\\[4ex]

Furthermore, I recommend including a declaration of potential conflicts of interest in
the manuscript. This may be particularly important in light of the significance of the
findings from the study for the continued operation of industrial companies.\\[2ex]

\response{We have added such a declaration at the end of the paper:\\[2ex]

\textit{\Paste{r.1.c}}
}

@@

              Many thanks for this comment. Ideally, we would of course use real-time
              data. For example, several studies have used smartphone tracking data for
              this purpose. However, any such data are not detailed enough for our
              requirements because they do not provide any information about
              \textit{who} is meeting with each other. These dimensions make up our
              contact networks, which are absolutely crucial.
